The \dealii Library, Version 9.1

### 2019-06-08 9.1/paper.tex
Add comments

>>>>

  \textbf{
  Matthias. These are suggestions. Feel free to ignore them. I'm planing
  to do maxwell simulations with \dealii{} and I would like to understand
  the advantages of NedelecSZ.
  \begin{itemize}
  \item I'm not sure what is wrong
  with the former Nedelec element. Is it correct what I wrote? Feel free
  to edit it.
  \item This new NedelecSZ element works with adaptive mesh refinement?
  \item If it does not work with hanging nodes. Would it be possible to
  explain in a couple of sentences what is left to make it work with
  hanging nodes?.
  \end{itemize}
  }
